Recursive Neural Network Part-of-Speech Tagger

### 2013-12-20 paper/paper.tex
Write more introduction.

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}

@@

Recursive neural networks are neural network models that allow for cyclic connections between neurons.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2014}
\usepackage{times}
\usepackage{url}
\usepackage{latexsym}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{braket}

@@

\subsection{Recursive Neural Networks}

Recursive neural networks are neural network models that allow for cyclic connections between neurons. Generally, recursive networks can have very complex structures, but for our application to part-of-speech tagging, we consider a restricted structure in which the network observes its own output on prior sentence context while consuming as input the current word in order to produce a classification label representing the current word's part of speech tag. When training the network or using the network to classify an example sentence, we temporarily unroll the recurrent network into an equivalent, feedforward multilayer perceptron with weight matrix shared between all layers.

Our network structure is a simplification of the more general binary tree structure trained by Socher et al. (2010) which iteratively constructs a parse tree by evaluating, at the base case, the best combinations of pairs of words, and subsequently the best combinations of pairs of previous combinations. Instead, we construct a linear, degenerate tree by always pairing the current word (on the right) to the previous combination (on the left) of prior sentence context and the prior word to obtain a phrase representation. We hope that phrase representation captures both the possible parts-of-speech for the current word and distinguishing context that allows an accurate choice of the correct part-of-speech.

\subsection{Distributed Word Representations}

Underlying the entire model are distributed word representations, which we use directly from the research of Collobert and Weston (2011), downloadable from their website (\hyperlink{http://ronan.collobert.com/senna/}{ronan.collobert.com/senna}). Distributed word representations are dense vectors embedded within an $n$-dimensional vector space and differ from sparse, ``one-hot" vectors embedded within a $\left\vert\mathcal{V}\right\vert$-dimensional vector space, where $\mathcal{V}$ is the vocabulary of the language domain.
